The markings of the trade: exploring the patterns of olive oil production in Roman Baetica

### 2018-07-16 Paper/jaccardbaetica.tex
correct errors
modify number stamps

We studied a dataset of 3787 stamps collected from different Dressel 20 amphora workshops in Baetica province. The stamp database was compiled by CEIPAC database \citep{remesal_centro_2015} (see CEIPAC database here \url{http://romanopendata.eu}). However, approximately the 70 \% of stamps cannot be tested due to fragmentation or incomplete information. Consequently, we discard integrate the fragmented stamps in our dataset. We finally filter a total sample of 987 stamps comprised of 131 different stamps from 81 workshops.

@@

%%\subsection{Jaccard distance}
%The dataset was analysed using a statistic method as Jaccard distance. This method allows to measure the dissimilarity by calculating the presence of sets (CITAR). In our case, Jaccard distance was used to compute the mutual presence of traits in the amphora stamps but it does not consider the number of absences. A comparison was done with the distance of the workshops to identify whether there was an association between stamps and spatial distance amongst workshops.

\subsection{Quantifying the cultural diversity: Morisita-Horn index}

@@

\xavi{no pillo demasiado lo que comentas de "groupings of similar stamps were not found in the cluster".}
\xavi{Si usas esos colores aquí y en la figura anterior entonces deberías usarlos también en el mapa.}

>>>>

We studied a dataset of 3798 stamps collected from different Dressel 20 amphora workshops in Baetica province. The stamp database was compiled by CEIPAC database \citep{remesal_centro_2015} (see CEIPAC database here \url{http://romanopendata.eu}). However, approximately the 70 \% of stamps cannot be tested due to fragmentation or incomplete information. Consequently, we discard integrate the fragmented stamps in our dataset. We finally filter a total sample of 987 stamps comprised of 130 different stamps from 81 workshops.

%3798 = base de datos sin limpiar
%3791 = base de datos limpiada con cleanstamp.py
%3787 = no sé a qué corresponde pero es archivo baetica.csv

@@

\subsection{Quantifying the cultural diversity}

\subsubsection{Jaccard distance}

The dataset was analysed using a statistic method as Jaccard distance. This method allows to measure the dissimilarity by calculating the presence of sets (CITAR). In our case, Jaccard distance was used to compute the mutual presence of traits in the amphora stamps but it does not consider the number of absences. A comparison was done with the distance of the workshops to identify whether there was an association between stamps and spatial distance amongst workshops.

(EXTENDER)

\subsubsection{Morisita-Horn index}

@@

%\xavi{no pillo demasiado lo que comentas de "groupings of similar stamps were not found in the cluster".}
%\xavi{Si usas esos colores aquí y en la figura anterior entonces deberías usarlos también en el mapa.}
